Network Configuration Synthesis with Abstract Topologies

### 2016-11-07 paper/abstraction/paper.tex
edits

Such simulations provide some assurance that the templates work correctly for the simulated topologies but little assurance for other topologies that may arise after the network evolves. It is hard to predict all future topologies in advance, templates that work for one topology may not work for seemingly-inconsequential variations.

Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy. One might think that the same templates (with different database entries) can be used for both topologies, but that is not true. For instance, consider templates that disallow ``valley" paths, which go up, down, and then up again; it is a common to disallow valley paths in a data center because they are longer than shortest paths. These templates will work perfectly for Figure~\ref{fig:example}, but violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:motivation}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces  the covering prefix PG (because it gets routes for P[3--4]). In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single link failure because spine routers have two links to each pod.

Thus, today, operators test templates for each topology change. For some changes, they may discover that their old templates will not work anymore. ~\dpw{Note: This is going to be true for Methane too.} ~\ratul{Not really; our abstract topologies encode all possible future topologies}
This discovery is highly problematic because changing a template may cause a configuration change of all the devices that use that template---an unacceptable disruption in many cases.  When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
Such patches reintroduce the complexity and errors that templates were meant to prevent.

@@

\sysname is a system to generate provably-correct templates.  As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and
connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
\sysname provides strong guarantees about its templates:
(1) the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the given abstract topology; and (2) if nodes or edges are added or removed in a way compatible
with the abstract topology, only configurations of adjacent devices ever need to be updated.

>>>>

Such simulations provide some assurance that the templates work correctly for the simulated topologies but little assurance for other topologies that may arise after the network evolves. Templates that work for one topology may not work for seemingly-inconsequential variations.  Unfotunately, currently,
there is no way to predict which variations will behave correctly for a given set of templates.
Worse, when operators discover their old templates no longer work, a change to a template will
cause a change to all devices that use that template---an unacceptable disruption in many cases.  When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
Such patches reintroduce the complexity and errors that templates were meant to prevent.

%% For some changes, they may discover that their old templates will not work anymore. ~\dpw{Note: This is going to be true for Methane too.} ~\ratul{Not really; our abstract topologies encode all possible future topologies} ~\dpw{Our abstract topologies precisely define a set of topologies for which our 
%% This discovery is highly problematic because changing a template may cause a configuration change of all the devices that use that template---an unacceptable disruption in many cases.  When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
%% Such patches reintroduce the complexity and errors that templates were meant to prevent.

Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy. One might think that the same templates (with different database entries) can be used for both topologies, but that is not true. For instance, consider templates that disallow ``valley" paths, which go up, down, and then up again; it is a common to disallow valley paths in a data center because they are longer than shortest paths. These templates will work perfectly for Figure~\ref{fig:example}, but violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example2}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:motivation}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces  the covering prefix PG (because it gets routes for P[3--4]). In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single link failure because spine routers have two links to each pod.

%% Thus, today, operators test templates for each topology change. For some changes, they may discover that their old templates will not work anymore. ~\dpw{Note: This is going to be true for Methane too.} ~\ratul{Not really; our abstract topologies encode all possible future topologies} ~\dpw{Our abstract topologies precisely define a set of topologies for which our 
%% This discovery is highly problematic because changing a template may cause a configuration change of all the devices that use that template---an unacceptable disruption in many cases.  When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
%% Such patches reintroduce the complexity and errors that templates were meant to prevent.

@@

\sysname is a system for generating provably-correct templates.  As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and
connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
\sysname provides strong guarantees about its templates:
(1) the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the given abstract topology; and (2) if nodes or edges are added or removed in a way compatible
with the abstract topology, only configurations of adjacent devices ever need to be updated.
